---
title: "iteration_and_listcols"
author: "Matthew Lawlor"
date: "11/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)

set.seed(1)
```

## lists

You can put anything in a list

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat = matrix(1:8, nrow =2, ncol = 4),
  summary = summary(rnorm(100))
)
```

```{r}
l
l$vec_numeric
l[[1]] ##first list element
mean(l[["vec_numeric"]])
l[["vec_numeric"]][1:3]
```

## `for` loop

create a new list

```{r}
list_norm = 
  list(
    a = rnorm(20, mean =3, sd =1),
    b = rnorm(30, mean =0, sd =5),
    c = rnorm(40, mean =10, sd =0.2),
    d = rnorm(20, mean =-3, sd =1)
  )
```

```{r}
list_norm[[1]]
```

Pause and get my old function

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

I can apply that function to each list element

```{r}
mean_and_sd (list_norm[[1]])
mean_and_sd (list_norm[[2]])
mean_and_sd (list_norm[[3]])
mean_and_sd (list_norm[[4]])
```

Let's use a `for` loop

```{r}
output = vector("list", length = 4)

for (i in 1:4) {

  output[[i]] = mean_and_sd(list_norm[[i]])

}
```

## Let's try map!

```{r}
output = map(list_norm, mean_and_sd)
```

What if you want a different function

```{r}
output = map(list_norm, median)
```

```{r}
output = map_dbl(list_norm, median)##gives a vector instead of a list
```

Create an ID vector  

```{r}
output = map_df(list_norm, mean_and_sd, .id = "input")##creates a tibble, id creates an id vector
```

## list columns!

```{r}
listcol_df =
  tibble(
   name = c("a", "b", "c", "d"),
   samp = list_norm
  )
```

```{r}
listcol_df %>% pull(name)
listcol_df %>% pull(samp)

listcol_df %>% 
  filter(name == "a")
```


Let's try some operations (this is inefficient but it works)

```{r}
mean_and_sd(listcol_df$samp[[1]]) ##$ same as "pull"
mean_and_sd(listcol_df$samp[[2]])
mean_and_sd(listcol_df$samp[[3]])
```

Can I just map?

```{r}
map(listcol_df$samp, mean_and_sd)
```

Can I add a list column from output?

```{r}
listcol_df =
  listcol_df %>% 
  mutate(
    summary = map(samp, mean_and_sd),
    medians = map_dbl(samp, median)
  )
```

## Weather Data in list columns

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Get our list columns

```{r}
weather_nest = 
  weather_df %>% 
  nest(data = date:tmin)
```


```{r}
weather_nest %>%  pull(name)
weather_nest %>%  pull(data)

weather_nest$data[[1]]
```

Suppose I want to regress `tmax` on `tmin` for each station

This example works...but would need to be repated for each tibble within the df
```{r}
lm(tmax ~ tmin, data = weather_nest$data[[1]])
```

But better, let's write a function

```{r}
weather_lm = function(df) {

  lm(tmax ~ tmin, data = df)  
  
}

##does it work?
weather_lm(weather_nest$data[[1]])
```

Can then create a for loop to repeat

```{r}

output = vector("list", 3)

for (i in 1:3) {
  
  output[[i]] = weather_lm(weather_nest$data[[i]])
    
}
```

But would be easier using map

```{r}
map(weather_nest$data, weather_lm)
```

What about adding a map in a list column

```{r}
weather_nest =
weather_nest  %>% 
  mutate(
    models = map(data, weather_lm)
  )

weather_nest$models
```


