---
title: "writing_functions"
author: "Matthew Lawlor"
date: "11/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
```

```{r}
set.seed(1)
```

## Do something simple

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)##computes a z-score
```

I want a function to compute z-scores

```{r}
z_scores = function(x) {

 if(!is.numeric(x)) {
   stop("Input must be numeric")
 }
   
 if(length(x) < 3) {
   stop("Must have at least three numbers")
 }
  
 z = (x - mean(x)) / sd(x)
  
  return(z)
  
}

z_scores(x_vec)
```

Try my function on some other things. These should give errors!

```{r, error = TRUE}
z_scores(3)
z_scores("my name is matt")
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
```

## Multiple outputs

```{r}
mean_and_sd = function(x) {

 if(!is.numeric(x)) {
   stop("Input must be numeric")
 }
   
 if(length(x) < 3) {
   stop("Must have at least three numbers")
 }
  
 mean_x = mean(x)
 sd_x = sd(x)
  
 tibble(##instead of return, can also use list
   mean = mean_x,
   sd = sd_x
   )
  
}
```

Check that the function works.

```{r}
mean_and_sd(x_vec)
```

## Multiple inputs

I'd like to do this with a function
```{r}
sim_data = 
  tibble(
    x = rnorm(100, mean = 4, sd = 3)
  )

sim_data %>% 
  summarize(
  mean = mean(x),
  sd = sd(x)
  )
```

The function
```{r}
sim_mean_sd = function(samp_size, mu, sigma) {
  
  sim_data = 
    tibble(
      x = rnorm(n = samp_size, mean = mu, sd =        sigma)
  )

  sim_data %>% 
  summarize(
  mean = mean(x),
  sd = sd(x)
  )
  
}

sim_mean_sd(100, 6, 3)
```

## Let's review Napoleon Dynamite

```{r, eval = FALSE}

url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = 
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )

```

What about the next page of reviews...

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2" ##have changed page 1 to 2

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews_page_2 = 
  tibble( ##new tibble but this is inefficient
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
```

Let's turn that code into a function

```{r}
read_page_reviews = function(url) {

  html = read_html(url)

  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()

  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()

  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()

  reviews = 
    tibble(
      title = review_titles,
      stars = review_stars,
      text = review_text
    )
  
  reviews
}
```


Try my function!

```{r}
dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=3"

read_page_reviews(dynamite_url)
```

Let's read a few pages of reviews

```{r}
dynamite_url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

dynamite_urls = str_c(dynamite_url_base, 1:5)

all_reviews = ## this is better than copy pasting the function code, but still running into issue with repeating code
  bind_rows(
    read_page_reviews(dynamite_urls[1]),
    read_page_reviews(dynamite_urls[2]),
    read_page_reviews(dynamite_urls[3]),
    read_page_reviews(dynamite_urls[4]),
    read_page_reviews(dynamite_urls[5])
  )
```


## Mean scoping example

```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```

## Functions as arguments

```{r}
my_summary = function(x, summ_func) {
  
  summ_func(x)
  
}

x_vec = rnorm(100, 3, 7)

##use the summary functions
mean(x_vec)
median(x_vec)
## or we can use the function we just created
my_summary(x_vec, mean)
```

